---
title: "Final Presentation"
toc: true
toc-location: right
execute:
  echo: false
  warning: false
  message: false
params:
  number: 7
  weight: '5%'
---

```{r}
#| label: setup

source(here::here("_common.R"))

rubric <- read_csv(here::here('rubrics', '7-final-presentation.csv'))
maxPoints <- rubric %>%
    filter(rating == "Excellent") %>%
    summarise(max = sum(maxPoints)) %>%
    pull(max)
```

```{r child = here::here("fragments", "project.qmd")}
```


Make a slideshow presentation of your findings in your final report. You may do one of the following: 

- Create a video recording of your presentation and publish it on the web (e.g. via Youtube, Vimeo, etc.).
- Present your presentation live in class.

We will watch all the presentations together during the period scheduled for the exam.

Below is a list of specific items your presentation should include.

# 1. Format

- Your presentation should be no longer than 10 minutes in length.
- Each team member must present at least one slide.
- You may use as many slides as you feel helps you communicate your ideas (but keep the 10 minute limit in mind).
- Your title slide should include the project title, team member names, and the presentation date: December 10, 2025.
- All slides should be numbered in the bottom-left or bottom-right corners.
- Review the slide design guidelines discussed in [class](https://madd.seas.gwu.edu/2026-Fall/class/14-communicating-results.html) as a check list when designing your slides.

# 2. Recording strategies

If you choose to record your presentation, I recommend using Zoom. Have someone share their screen showing the slides and talk over the slides while recording the call.

Another option is to use a screen recording program, such as Quicktime (mac only), to record a screen recording on someone talking over the slides, though this may be challenging if not all teammates can be in the same room.

# 2. Content

Your slides do not need to include the detailed code used to conduct your analysis - that should be accessible from your report. Rather, the purpose of your presentation is to present the "big picture" overview and results from your project. You should discuss:

1. An introduction of your product / policy (similar to the introduction in your report).
2. A brief overview of your survey:
    - At least one slide depicting an example choice question
    - At least one slide with some summary stats about your sample (e.g., sample size, etc.)
3. Your main findings:
    - A slide describing your utility model
    - Polished charts of WTP, market simulations, sensitivity analyses.
    - For your market simulation(s), you must show a table showing the attributes used in the simulation(s).
    - Your recommendations based on your findings.

# 4. Publish 

If you recorded a video, publish your video recording on the web (e.g. via Youtube, Vimeo, etc.), then **send a link to the published video in a DM to Professor Helveston on slack.**

Only one team member needs to publish the video.

# 5. Submit

Push your slides (as a pdf, pptx, or qmd -- whatever you used to make them) to your team's repo (`madd-f26/madd-team-<letter>`, where `<letter>` is your team letter), inside the `7-final-presentation/` folder, using GitHub Desktop.

::: {.callout-note title="Remember"}
This deliverable isn't submitted until it's **pushed** to your team repo. Any team member can push -- there's no need to designate just one person. Go look at your repo on GitHub.com and confirm the work is actually there before you call this done.
:::

# Grading Rubric

**`r maxPoints` Total Points**

```{r, echo=FALSE}
make_rubric(rubric)
```
